Scikit-learn: API design for machine learning

### 2013-06-17 paper.tex
external estimators covered, remove todo
partial application and meta-estimators

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, default hyper-parameter values are provided for all built-in
estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible
\textit{out-of-box} for non-experts. Finally, the constructor of an estimator
never performs any actual learning (this is the role of the \texttt{fit} method,
see below).  Its only goal is to set the parameter values and freeze the
behavior of the estimator.

The estimator interface defines a \texttt{fit} method. This method is called
with training data (e.g., supplied as two arrays \texttt{X\_train} and
\texttt{y\_train} in supervised learning estimators). Its task is to run a
learning algorithm and to determine model- specific parameters from the training
data and set these as attributes on the estimator object. As a convention, the
parameters learned by an estimator are exposed as public attributes whose name
is suffixed with a trailing underscore (e.g., \texttt{coef\_} for the
learned coefficients of a linear model).

@@

Finally, let us also note that the \texttt{fit} method always returns the estimator
it was called on, hence making method chaining possible.  Using this technique,
we can thus rewrite the \texttt{StandardScaler} example above in a single line:
\begin{pythoncode}
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{pythoncode}
In addition, \texttt{fit(X\_train).transform(X\_train)} can further
be rewritten as \texttt{fit\_transform(X\_train)}.  Combining the \texttt{fit}
and \texttt{transform} methods into a single method \texttt{fit\_transform}
allows to share computations, which often makes a huge difference in practice.
In the same spirit, \sklearn sometimes provides the
\texttt{fit\_predict} method for combining the \texttt{fit} and \texttt{predict}
methods. This is especially useful for retrieving cluster predictions with
respect to the training data \texttt{X\_train} in clustering algorithms.

@@

\textcolor{red}{TODO: Point out that any external estimator can be used as base
estimator thanks to duck typing}

>>>>

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, default hyper-parameter values are provided for all built-in
estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible
\textit{out-of-box} for non-experts. Finally, the constructor of an estimator
never performs any actual learning (this is the role of the \texttt{fit} method,
see below).  Its only goal is to set the parameter values and freeze the
behavior of the estimator.
Initializing and fitting an estimator object
proceeds in a way that is similar to partial function application:
an estimator can be considered a function
that maps hyperparameter settings to an actual learning algorithm.
The advantage of this API
over one where the object initializer would perform the learning
will become especially apparent in Section~\ref{sec:advanced-api}.

The estimator interface defines a \texttt{fit} method. This method is called
with training data (e.g., supplied as two arrays \texttt{X\_train} and
\texttt{y\_train} in supervised learning estimators). Its task is to run a
learning algorithm and to determine model- specific parameters from the training
data and set these as attributes on the estimator object. As a convention, the
parameters learned by an estimator are exposed as public attributes whose name
is suffixed with a trailing underscore (e.g., \texttt{coef\_} for the
learned coefficients of a linear model).
The return value of \texttt{fit} is always the object it was called on,
which now serves as a model of its input
and can be used to perform predictions or transformations of input data.

@@

Additionally, by leveraging that fact that \texttt{fit}
always returns the estimator it was called on,
the \texttt{StandardScaler} example above
can be rewritten in a single line using a ``method chaining'' style:
\begin{pythoncode}
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{pythoncode}
Finally, \texttt{fit(X\_train).transform(X\_train)} can further
be rewritten as \texttt{fit\_transform(X\_train)}.  Combining the \texttt{fit}
and \texttt{transform} methods into a single method \texttt{fit\_transform}
allows to share computations, which often makes a huge difference in practice.
In the same spirit, clustering algorithms provide a
\texttt{fit\_predict} method
that is equivalent to \texttt{fit} followed by \texttt{predict},
and thus returns the cluster labels assigned to the training data samples.

@@

Some machine learning algorithms are most naturally expressed
as modification or extensions of other, simpler algorithms.
Examples include ensemble estimators
and various multiclass and multilabel classification schemes.
Such algorithms are implemented as so-called ``meta-estimators'',
that take an estimator as input and use that to perform learning and prediction.

As an example, a logistic regression classifier
by default uses a one-vs.-rest (aka one-vs.-all) scheme internally
for performing multiclass classification.
If multiclass classification based on error-correcting codes
\citep{dietterich1995solving} is desired instead,
this can achieved with an \texttt{OutputCodeClassifier}
that wraps a \texttt{LogisticRegression}:
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression
from sklearn.multiclass import OutputCodeClassifier

ecoc_lr = OutputCodeClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}

% TODO: show a grid search on this estimator
